Guarded Recursion in Agda via Sized Types

### 2019-01-29 code-oneclock-paper/latex/paper.tex
minor changes in Sec 4

To interpret simple type theory, we also need to give the context operations, simple type formers, and operations on substitutions.
Since their definitions are standard, we do not discuss them formally.
For each of them, we need to make a case distinction based on the clock context.
For example, the empty context is interpreted by the unit type and terminal presheaf depending on the clock context.
We use the operations on presheaves defined in \Cref{sec:presheaves} to interpret simple type formers.
\input{CloTT/TypeFormers/FunctionType}

>>>>

We also need to provide a semantic version of 
%To interpret simple type theory, we also need to give 
the context operations, the simple type formers and the operations on substitutions.
Since their definitions are standard, we do not discuss them in detail.
For each of them, we need to make a case distinction based on the clock context.
For example, the empty variable context \IC{•} is interpreted either as the unit type
or as the terminal presheaf, depending on the clock context.
We use the operations on presheaves defined in \Cref{sec:presheaves} to interpret simple type formers.
\input{CloTT/TypeFormers/FunctionType}
